systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-20 paper/trunk/systemfit_summary.tex
two modifications in the introduction and in the summary due to the inclusion of section "testing reliability" (in the previous revision)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@622 591db2bd-e0a0-4d22-8c19-2192dbb7da31

In this article, we have described some of the basic features of the
\pkg{systemfit} package for estimation of linear systems of
equations with various estimation methods.
Many details of the estimation can be controlled by the user.
Furthermore, the package provides some statistical tests
for parameter restrictions and consistency of 3SLS estimation.
It has been tested on a variety of datasets and has produced satisfactory
for a few years.%
\footnote{
The code to replicate results published in the literature is given
in the documentation of the cooresponding data sets
included in the \pkg{systemfit} package
(see the documentation of \code{GrunfeldGreen}, \code{GrunfeldTheil},
\code{KleinI} and \code{kmenta}).
}
While the \pkg{systemfit} package performs the basic fitting methods,
more sophisticated tools exist.
We hope to implement missing functionalities
in the near future.
Some of these are discussed in the following.

>>>>

In this article, we have described some of the basic features of the
\pkg{systemfit} package for estimation of linear systems of
equations with various estimation methods.
Many details of the estimation can be controlled by the user.
Furthermore, the package provides some statistical tests
for parameter restrictions and consistency of 3SLS estimation.
It has been tested on a variety of datasets and has produced satisfactory
for a few years.
While the \pkg{systemfit} package performs the basic fitting methods,
more sophisticated tools exist.
We hope to implement missing functionalities
in the near future.
Some of these are discussed in the following.
